Housing Default Handovers

### 2024-03-27 minos/validation/housing_handovers.Rmd
getting sensible looking handovers for net income, ncars, and ncigs

net.income.spag <- rbind(raw.inc, base.inc)

density_ridges(net.income.spag, 'net_hh_income',
               save=TRUE, 
               save.path=save.path)
handover_boxplots(raw.dat, base.dat, 'net_hh_income')

@@

# rent
handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
               save=TRUE, 
               save.path=save.path)

# mortgage
handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
               save=TRUE, 
               save.path=save.path)

#council tax
handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
               save=TRUE, 
               save.path=save.path)

# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
density_ridges(inc.spag, 'oecd_equiv',
               save=TRUE, 
               save.path=save.path)

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

sf12.spag <- rbind(raw.sf12, base.sf12)

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```

## Financial Situation

```{r}
raw.financial_situation <- raw.dat %>%
  dplyr::select(pidp, time, financial_situation) %>%
  group_by(time, financial_situation) %>%
  count() %>%
  mutate(source = 'final_US')

base.financial_situation <- base.dat %>%
  dplyr::select(pidp, time, financial_situation) %>%
  group_by(time, financial_situation) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
financial_situation <- rbind(raw.financial_situation, base.financial_situation)
financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)

# Now plot
ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

financial_situation.norm <- financial_situation %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial situation') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'financial_situation.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm)
```

## Housing Quality

```{r}
raw.housing <- raw.dat %>%
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
housing <- rbind(raw.housing, base.housing)
housing$housing_quality <- as.factor(housing$housing_quality)

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

housing.norm <- housing %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'housing_quality.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.housing, base.housing, housing, housing.norm)
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Housing Tenure

```{r}
raw.tenure <- raw.dat %>%
  dplyr::select(pidp, time, housing_tenure) %>%
  group_by(time, housing_tenure) %>%
  count() %>%
  mutate(source = 'final_US')

base.tenure <- base.dat %>%
  dplyr::select(pidp, time, housing_tenure) %>%
  group_by(time, housing_tenure) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
tenure <- rbind(raw.tenure, base.tenure)
tenure$housing_tenure <- as.factor(tenure$housing_tenure)

# Now plot
ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Tenure', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

tenure.norm <- tenure %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Tenure') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'housing_tenure.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.tenure, base.tenure, tenure, tenure.norm)
```

## Neighbourhood Safety

```{r}
raw.neighbour <- raw.dat %>%
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
neighbour <- rbind(raw.neighbour, base.neighbour)
neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)

# Now plot
ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
  xlab('Year') +
  ylab('Count')

neighbour.norm <- neighbour %>%
  group_by(time) %>%
  filter(neighbourhood_safety != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Neighbourhood Safety') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'neighbourhood_safety.png',
       plot = last_plot(),
       path = save.path)
}

#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Loneliness

```{r}
raw.loneliness <- raw.dat %>%
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
loneliness <- rbind(raw.loneliness, base.loneliness)
loneliness$loneliness <- as.factor(loneliness$loneliness)

# Now plot
ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness', subtitle = 'Counts by level') +
  xlab('Year') +
  ylab('Count')

loneliness.norm <- loneliness %>%
  group_by(time) %>%
  filter(loneliness != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'loneliness.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, loneliness)
# base.s <- base.dat %>%
#   select(pidp, age, time, loneliness)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'loneliness',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Nutrition Quality

TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
handover_lineplots(raw.dat, base.dat, 'nutrition_quality')

# Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.nut2 <- raw.dat %>%
#   dplyr::select(pidp, time, nutrition_quality) %>%
#   filter(pidp %in% raw.wave1) %>%
#   filter(nutrition_quality >= 0) %>%
#   group_by(time) %>%
#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.nut2 <- base.dat %>%
#   dplyr::select(pidp, time, nutrition_quality) %>%
#   filter(pidp %in% raw.wave1) %>%
#   group_by(time) %>%
#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
# 
# # Now plot
# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Nutrition Quality') +
#   xlab('Year') +
#   ylab('Nutrition Quality')
# 
# if (shall.we.save) {
#   ggsave(filename = 'nutrition_quality_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
#     nutrition_quality2)
```

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, nutrition_quality)
# base.nut <- base.dat %>%
#   select(pidp, age, time, nutrition_quality)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'nutrition_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "nutrition_quality", 
#                save = T, 
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

## Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
phealth <- rbind(raw.phealth, base.phealth)

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')

## Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.phealth2 <- raw.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

phealth2 <- rbind(raw.phealth2, base.phealth2)

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health') +
  xlab('Year') +
  ylab('Average')

if (shall.we.save) {
  ggsave(filename = 'physical_health_wav1.png',
       plot = last_plot(),
       path = save.path)
}

#raw.phealth.check <- raw.dat %>%
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

#base.phealth.check <- base.dat %>%
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
#rm(raw.phealth.check, base.phealth.check)
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, phealth)
# base.s <- base.dat %>%
#   select(pidp, age, time, phealth)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'phealth',
#              save = shall.we.save,
#              save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Education

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')

>>>>

net.income.spag <- rbind(raw.inc, base.inc)
net.income.spag <- net.income.spag[which(net.income.spag$net_hh_income<50000), ]
density_ridges(net.income.spag, 'net_hh_income',
               save=TRUE, 
               save.path=save.path)
handover_boxplots(raw.dat, base.dat, 'net_hh_income')

@@

# rent
handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'hh_rent',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, 'hh_rent',
               save = shall.we.save,
               save.path = save.path)
# mortgage
handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1 & raw.inc$hh_mortgage<5000), ], base.inc[which(base.inc$hh_mortgage>1 & base.inc$hh_mortgage<5000), ], 'hh_mortgage')
handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
density_ridges(inc.spag[which(inc.spag$hh_mortgage>1 & inc.spag$hh_mortgage<5000), ], 'hh_mortgage',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'hh_mortgage',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, "hh_mortgage",
               save = shall.we.save,
               save.path = save.path)
#council tax
handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
               save=TRUE, 
               save.path=save.path)
spaghetti_plot(net.income.spag.sample, 'council_tax',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, "council_tax",
               save = shall.we.save,
               save.path = save.path)

# oecd equivalence scale. 
#TODO not fully transitioned yet for leaving the nest.
handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
density_ridges(inc.spag, 'oecd_equiv',
               save=TRUE, 
               save.path=save.path)

@@

<!-- ```{r} -->
<!-- raw.sf12 <- raw.dat %>% -->
<!--   select(pidp, age, time, SF_12) -->
<!-- base.sf12 <- base.dat %>% -->
<!--   select(pidp, age, time, SF_12) -->

<!-- sf12.spag <- rbind(raw.sf12, base.sf12) -->

<!-- sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ] -->
<!-- spaghetti_plot(sf12.spag.sample, 'SF_12', -->
<!--                save = shall.we.save, -->
<!--                save.path = save.path) -->
<!-- spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12', -->
<!--                save = shall.we.save, -->
<!--                save.path = save.path) -->

<!-- density_ridges(sf12.spag, "SF_12",  -->
<!--                save = T,  -->
<!--                save.path = save.path) -->

<!-- rm(raw.sf12, base.sf12, sf12.spag) -->
<!-- ``` -->

<!-- ## Financial Situation -->

<!-- ```{r} -->
<!-- raw.financial_situation <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, financial_situation) %>% -->
<!--   group_by(time, financial_situation) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.financial_situation <- base.dat %>% -->
<!--   dplyr::select(pidp, time, financial_situation) %>% -->
<!--   group_by(time, financial_situation) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- financial_situation <- rbind(raw.financial_situation, base.financial_situation) -->
<!-- financial_situation$financial_situation <- as.factor(financial_situation$financial_situation) -->

<!-- # Now plot -->
<!-- ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Financial Situation', subtitle = 'Counts by Level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- financial_situation.norm <- financial_situation %>% -->
<!--   group_by(time) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Financial situation') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'financial_situation.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm) -->
<!-- ``` -->

<!-- ## Housing Quality -->

<!-- ```{r} -->
<!-- raw.housing <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, housing_quality) %>% -->
<!--   group_by(time, housing_quality) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.housing <- base.dat %>% -->
<!--   dplyr::select(pidp, time, housing_quality) %>% -->
<!--   group_by(time, housing_quality) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- housing <- rbind(raw.housing, base.housing) -->
<!-- housing$housing_quality <- as.factor(housing$housing_quality) -->

<!-- # Now plot -->
<!-- ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Quality', subtitle = 'Counts by Level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- housing.norm <- housing %>% -->
<!--   group_by(time) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Quality') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'housing_quality.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- rm(raw.housing, base.housing, housing, housing.norm) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- # raw.s <- raw.dat %>% -->
<!-- #   select(pidp, age, time, housing_quality) -->
<!-- # base.s <- base.dat %>% -->
<!-- #   select(pidp, age, time, housing_quality) -->
<!-- #  -->
<!-- # spag <- rbind(raw.s, base.s) -->
<!-- #  -->
<!-- # spaghetti_plot(spag, 'housing_quality', -->
<!-- #                save = shall.we.save, -->
<!-- #                save.path = save.path) -->
<!-- #  -->
<!-- # rm(raw.s, base.s, spag) -->
<!-- ``` -->

<!-- ## Housing Tenure -->

<!-- ```{r} -->
<!-- raw.tenure <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, housing_tenure) %>% -->
<!--   group_by(time, housing_tenure) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.tenure <- base.dat %>% -->
<!--   dplyr::select(pidp, time, housing_tenure) %>% -->
<!--   group_by(time, housing_tenure) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- tenure <- rbind(raw.tenure, base.tenure) -->
<!-- tenure$housing_tenure <- as.factor(tenure$housing_tenure) -->

<!-- # Now plot -->
<!-- ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Tenure', subtitle = 'Counts by Level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- tenure.norm <- tenure %>% -->
<!--   group_by(time) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Tenure') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'housing_tenure.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- rm(raw.tenure, base.tenure, tenure, tenure.norm) -->
<!-- ``` -->

<!-- ## Neighbourhood Safety -->

<!-- ```{r} -->
<!-- raw.neighbour <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
<!--   group_by(time, neighbourhood_safety) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.neighbour <- base.dat %>% -->
<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
<!--   group_by(time, neighbourhood_safety) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- neighbour <- rbind(raw.neighbour, base.neighbour) -->
<!-- neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety) -->

<!-- # Now plot -->
<!-- ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- neighbour.norm <- neighbour %>% -->
<!--   group_by(time) %>% -->
<!--   filter(neighbourhood_safety != -9) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Neighbourhood Safety') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'neighbourhood_safety.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- # raw.s <- raw.dat %>% -->
<!-- #   select(pidp, age, time, neighbourhood_safety) -->
<!-- # base.s <- base.dat %>% -->
<!-- #   select(pidp, age, time, neighbourhood_safety) -->
<!-- #  -->
<!-- # spag <- rbind(raw.s, base.s) -->
<!-- #  -->
<!-- # spaghetti_plot(spag, 'neighbourhood_safety', -->
<!-- #                save = shall.we.save, -->
<!-- #                save.path = save.path) -->
<!-- #  -->
<!-- # rm(raw.s, base.s, spag) -->
<!-- ``` -->

<!-- ## Loneliness -->

<!-- ```{r} -->
<!-- raw.loneliness <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, loneliness) %>% -->
<!--   group_by(time, loneliness) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.loneliness <- base.dat %>% -->
<!--   dplyr::select(pidp, time, loneliness) %>% -->
<!--   group_by(time, loneliness) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- loneliness <- rbind(raw.loneliness, base.loneliness) -->
<!-- loneliness$loneliness <- as.factor(loneliness$loneliness) -->

<!-- # Now plot -->
<!-- ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Loneliness', subtitle = 'Counts by level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- loneliness.norm <- loneliness %>% -->
<!--   group_by(time) %>% -->
<!--   filter(loneliness != -9) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Loneliness') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'loneliness.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- # raw.s <- raw.dat %>% -->
<!-- #   select(pidp, age, time, loneliness) -->
<!-- # base.s <- base.dat %>% -->
<!-- #   select(pidp, age, time, loneliness) -->
<!-- #  -->
<!-- # spag <- rbind(raw.s, base.s) -->
<!-- #  -->
<!-- # spaghetti_plot(spag, 'loneliness', -->
<!-- #                save = shall.we.save, -->
<!-- #                save.path = save.path) -->
<!-- #  -->
<!-- # rm(raw.s, base.s, spag) -->
<!-- ``` -->

<!-- ## Nutrition Quality -->

<!-- TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11 -->

<!-- ```{r} -->
<!-- #  nutriton quality line/boxplots. -->
<!-- handover_boxplots(raw.dat, base.dat, 'nutrition_quality') -->
<!-- handover_lineplots(raw.dat, base.dat, 'nutrition_quality') -->
